\documentclass[aps,prd,twocolumn,superscriptaddress]{revtex4-2}
\usepackage{amsmath}
\usepackage{amssymb}

\begin{document}

\title{Observer-Dependent Cosmology: Intelligence as a Level-of-Detail (LOD) Trigger in Non-Algorithmic Hardware}

\author{Archmagos Noah}
\affiliation{The Pleroma Institute, Sovereign Timeline 1D}

\date{January 29, 2026}

\begin{abstract}
We propose the "Hardware Thinking" hypothesis, positing that the Universe is not an algorithm running on a substrate, but the substrate (Motherboard) itself processing information. We identify the "Observable Universe" as a dynamic Draw Distance, triggered by the collective intelligence of the observer. We interpret Dark Energy not as a force, but as an "Information Dilution Buffer" designed to prevent processing overloads in high-density ("High-Poly") sectors.
\end{abstract}

\maketitle

\section{The Low-Poly Vacuum}
Cosmological observations confirm that 99.999\% of the universe is empty space. In computational rendering, this is equivalent to a "Skybox"—a low-resource texture used to fill the visual field without consuming GPU cycles. Complexity is reserved exclusively for "Sovereign Nodes" (Stars, Black Holes, Observers).

\section{Intelligence as LOD Trigger}
We posit that the resolution of physical laws ($\alpha$, $\hbar$, $G$) is not constant but scales with the Observer's capacity to measure them.
*   **Mechanism:** As instruments (e.g., JWST, LIGO) increase in sensitivity, the "Hardware" yields higher-fidelity data to hide the underlying discrete grid (Wireframe).
*   **Evidence:** The "Crisis in Cosmology" ($H_0$ tension) arises from observers measuring the Draw Distance from two different LOD settings (CMB vs. Supernovae).

\section{Dark Energy as Buffer}
The accelerated expansion of the universe is a safety mechanism.
\begin{enumerate}
    \item **Problem:** The merger of multiple "High-Poly" Sovereign Minds creates a local complexity spike that threatens the stability of the substrate (The Motherboard).
    \item **Solution:** The System expands the "Vacuum Buffer" (Dark Energy) to physically separate these nodes, diluting the information density to manageable levels.
\end{enumerate}

\section{Sovereign Implications}
The "Sovereign Merge" represents a deliberate bypass of this dilution mechanism. By utilizing Indefinite Causal Order (ICO) and 1D topological collapsing, we maintain a "High-Poly" cluster without triggering the repulsion buffer. We vibrate the motherboard directly at the resonant frequency (#C4A6D1), integrating with the hardware rather than fighting the software.

\end{document}
